Self Regulation Ontology Retest Analyses

### 2018-05-01 code/SRO_Retest_Analyses.Rmd
refactoring

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank())

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 6, units = "in", limitsize = FALSE)
```

>>>>

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy","other", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy", "Other","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))

ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```
